---
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
---

### Data Exploration Report

Keeping the length of this section reasonable, the exploration report shown here contains the data from 1990. The report for the rest of the data is in the appendix of the final document.

#### Animal Strike Data

The first summary table shows the number of distinct items for each year regarding the Airline operators, Aircraft, Aircraft types, Aircraft mass types, and Engine types, which have been reported as being affected in an animal strike.

```{r 240-table-01, results = 'asis'}
setOfColumns <- c("dataYear",
                  "numberOfRecords",
                  "factorOPID",
                  "factopATYPE",
                  "factorAC_CLASS",
                  "factorAC_MASS",
                  "factorTYPE_ENG")

setOfColumnTitles <- c("Year",
                       "# of reports",
                       "Operators",
                       "Aircraft",
                       "Aircraft type",
                       "Aircraft mass type",
                       "Engine type")
  
printTable(Full = FALSE, 
           DataFile = "01_EXP_Animal_Strikes.rds", 
           ColumnNames = setOfColumns, 
           ColumnTitles = setOfColumnTitles)
```

The second summary table shows the number of distinct items for each year regarding the Time of day, Airports, States, Phase of flight, weather conditions (Sky and Precipitation), and the flag for showing if the pilot has been warned or not about birds / wildlife in the reports.

```{r 240-table-02, results = 'asis'}
setOfColumns <- c("dataYear",
                  "factorTIME_OF_DAY",
                  "factorAIRPORT_ID",
                  "factorSTATE",
                  "factorPHASE_OF_FLT",
                  "factorSKY",
                  "factorPRECIP",
                  "factorWARNED")

setOfColumnTitles <- c("Year",
                       "Time of day",
                       "Airports",
                       "States",
                       "Phase of flight",
                       "Sky",
                       "Precipitation",
                       "Warned")
  
printTable(Full = FALSE, 
           DataFile = "01_EXP_Animal_Strikes.rds", 
           ColumnNames = setOfColumns, 
           ColumnTitles = setOfColumnTitles)
```


The following graphs show the distributions of some of the selected distinct items summarized in the tables above.

```{r 240-showPlots-01, results='asis'}

imageLocation <- getDocInputDir()
DataField <- c("AC_CLASS",
               "AC_MASS", 
               "TYPE_ENG", 
               "TIME_OF_DAY", 
               "PHASE_OF_FLT", 
               "SKY", 
               "PRECIP")


for (i in 1:7) {
  targetFileName <- paste("/1990_AnimalStrike_", 
                          DataField[i],
                          "_01_Orig.png", 
                          sep="")
  targetFile <- paste(imageLocation, 
                      targetFileName, 
                      sep="")
  if (file.exists(targetFile) == TRUE){
    cat("![](",targetFile,")\n")
  } else {
    cat(targetFile, " not found!")
  }
  
}

```

#### Flight Data

The first summary table shows the number of distinct items for each year regarding the number of records, the carriers, and the origin and the destination airports.

```{r 240-table-03, results = 'asis'}
setOfColumns <- c("dataYear",
                  "numberOfRecords",
                  "factorCarrier",
                  "factorOrigin",
                  "factorOriginState",
                  "factorDest",
                  "factorDestState")

setOfColumnTitles <- c("Year",
                       "# of flights",
                       "# of carriers",
                       "Origin airports",
                       "Origin states",
                       "Destination airports",
                       "Destination states")
  
printTable(Full = FALSE, 
           DataFile = "02_EXP_Flight_Data.rds", 
           ColumnNames = setOfColumns, 
           ColumnTitles = setOfColumnTitles)
```


The second summary table shows the number of distinct items for each year the departure time group and distance between the airports.

```{r 240-table-04, results = 'asis'}
setOfColumns <- c("dataYear",
                  "factorDepTimeBlk",
                  "factorDistanceGroup")

setOfColumnTitles <- c("Year",
                       "Departure time block",
                       "Distance group")
  
printTable(Full = FALSE, 
           DataFile = "02_EXP_Flight_Data.rds", 
           ColumnNames = setOfColumns, 
           ColumnTitles = setOfColumnTitles)
```


The following graphs show the distributions of some of the selected distinct items summarized in the tables above.

```{r 240-showPlots-02, results='asis'}

imageLocation <- getDocInputDir()
DataField <- c("Carrier",
               "DistanceGroup")


for (i in 1:2) {
  targetFileName <- paste("/1990_FlightData_", 
                          DataField[i],
                          "_01_Orig.png", 
                          sep="")
  targetFile <- paste(imageLocation, 
                      targetFileName, 
                      sep="")
  if (file.exists(targetFile) == TRUE){
    cat("![](",targetFile,")\n")
  } else {
    cat(targetFile, " not found!")
  }
  
}

```
