---
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: true
---

### Rationale for Inclusion / Exclusion

The resolution of the issues found during the data quality verification includes the exclusion of certain records from the data sets originally provided by the Federal Aviation Administration and the United States Department of Transportation agencies. This section provides the summary of the changes on the data sets.

#### Animal Strike Data

The following columns are impacted by the selection criteria described in the data quality verification section:

* OPID
* AC_CLASS
* TYPE_ENG

Additionally the number of States in the data set is above the actual number of states of the U.S., so the data needs to be reduced to contain only the following states:

```{r 330-table-01, results = 'asis'}
#cat("\\begin{multicols}{2}\n\n")
#cat("\\begin{center}\n")

printStates()

#cat("\\end{center}\n")
#cat("\n\\end{multicols}\n\n")
```

#### Flight Data

The data in the Federal Aviation Administration Animal Strike Database is available only until 30-4-2016, so the flight data needs to be adjusted accordingly.

Additionally the number of States in the data set is above the actual number of states of the U.S., so the data needs to be reduced to contain only the following states:

```{r 330-table-02, results = 'asis'}
#cat("\\begin{multicols}{2}\n\n")
#cat("\\begin{center}\n")

printStates()

#cat("\\end{center}\n")
#cat("\n\\end{multicols}\n\n")
```

#### Airport Data

The data set contains the data of the currently operational and closed airports along with other aviation facilities (e.g.: balloon port), while I am interested of the data of only those airports which are operational, so the data of the closed airports and other type of aviation facilities needs to be removed.

The number of States in the data set is above the actual number of states of the U.S., so the data needs to be reduced to contain only the following states:

```{r 330-table-03, results = 'asis'}
#cat("\\begin{multicols}{2}\n\n")
#cat("\\begin{center}\n")

printStates()

#cat("\\end{center}\n")
#cat("\n\\end{multicols}\n\n")
```
