---
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: true
---

### Model Assessment

All the linear regression models will be assessed using the following criteria:

| Criteria              | Description                            |
|:----------------------|:---------------------------------------|
|Residuals|The expectation is that the residuals have a normal distribution, with a Median value close to 0.|
|Significance markings|A very low p-value is indicated as "***", while a " " is considered a high p-value. A lower p-value indicates that it's more unlikely that there is no relationship between the outcome and the predictor variable.|
|Standard error of the coefficient estimate|this value is measuring the variability in the coefficient estimate. The value is relative to the coefficient estimate, in general lower is better.|
|p-value|The predictor variable probability of being not relevant. Lower value is better, since it means that the predictor is relevant.|
|R-squared|It's the numeric representation of how well is the model fitting the data. In general higher is better, indicating a good correlation, but this does not mean causation.|

#### Model01-01 Assessment

\setmonofont{Courier New}
\setmainfont{Courier New}
```{r 450-ModelAssessment-01}
dataDir <- getDataDir()
RDSFileName <- "10_Model_01_01.rds"
RDSFile <- paste(dataDir,
                     "/",
                     RDSFileName,
                     sep = "")
model01 <- readRDS(file = RDSFile)
summary(model01)
cat("\n\n")
```
\setmonofont{Times New Roman}
\setmainfont{Times New Roman}

While the residuals seem to have a quite normal distribution none of the predictors is significant for the outcome. This model is not good, the remaining criteria do not need to be evaluated.

#### Model01-02 Assessment

\setmonofont{Courier New}
\setmainfont{Courier New}
```{r 450-ModelAssessment-02}
dataDir <- getDataDir()
RDSFileName <- "10_Model_01_02.rds"
RDSFile <- paste(dataDir,
                     "/",
                     RDSFileName,
                     sep = "")
model02 <- readRDS(file = RDSFile)
summary(model02)
cat("\n\n")
```
\setmonofont{Times New Roman}
\setmainfont{Times New Roman}

In the second model the residuals are not distributed normally and even though the predictor significance got a little bit better, the model is still not acceptable. Just like in the previous case, the remaining criteria do not need to be evaluated.

#### Model01-03 Assessment

\setmonofont{Courier New}
\setmainfont{Courier New}
```{r 450-ModelAssessment-03}
dataDir <- getDataDir()
RDSFileName <- "10_Model_01_03.rds"
RDSFile <- paste(dataDir,
                     "/",
                     RDSFileName,
                     sep = "")
model03 <- readRDS(file = RDSFile)
summary(model03)
cat("\n\n")
```
\setmonofont{Times New Roman}
\setmainfont{Times New Roman}

While this model has a much better predictor significance, the distribution of the residuals can't be accepted, making the model rejected.

#### Model01-04 Assessment

\setmonofont{Courier New}
\setmainfont{Courier New}
```{r 450-ModelAssessment-04}
dataDir <- getDataDir()
RDSFileName <- "10_Model_01_04.rds"
RDSFile <- paste(dataDir,
                     "/",
                     RDSFileName,
                     sep = "")
model04 <- readRDS(file = RDSFile)
summary(model04)
cat("\n\n")
```
\setmonofont{Times New Roman}
\setmainfont{Times New Roman}

The forth is the first model where the predictor significance seems to be really good, along with an acceptable level of r-squared values, but I still have to reject the model because of the distribution of the residuals.

#### Model01-05 Assessment

\setmonofont{Courier New}
\setmainfont{Courier New}
```{r 450-ModelAssessment-05}
dataDir <- getDataDir()
RDSFileName <- "10_Model_01_05.rds"
RDSFile <- paste(dataDir,
                     "/",
                     RDSFileName,
                     sep = "")
model05 <- readRDS(file = RDSFile)
summary(model05)
cat("\n\n")
```
\setmonofont{Times New Roman}
\setmainfont{Times New Roman}

The fifth model is showing the possibility of a higher significance of the airport location with a quite good residual distribution, but from interpretation point of you it's a bit misleading as well, since the regions and the states are overlapping, making the predictors incorrect from the domain point of view.

#### Model01-06 Assessment

\setmonofont{Courier New}
\setmainfont{Courier New}
```{r 450-ModelAssessment-06}
dataDir <- getDataDir()
RDSFileName <- "10_Model_01_06.rds"
RDSFile <- paste(dataDir,
                     "/",
                     RDSFileName,
                     sep = "")
model06 <- readRDS(file = RDSFile)
summary(model06)
cat("\n\n")

```
\setmonofont{Times New Roman}
\setmainfont{Times New Roman}

I consider the sixth and final model the best logistic regression model, as it has a quite normal residual distribution, very high significance for most of the predictors (some of the predictors are showing a very strong relation to the outcome) with good standard error for the predictors and very high r-squared values.

Taking into account that the model is a log-log model including categorical predictors (meaning that I used the natural log of the outcome and the continous predictor variables along with categorical predictors), the interpretation would go for the traffic originated from the airport as a one percent change in the originated traffic would be expected to have a 0.01518 percent change in the number of strikes is, compared to the number of strikes of Alaska.

### Revised Parameter Settings

Keeping the modelling task as simple as possible I did not change the parameter settings for the models, instead I've used different predictor combinations to get the best possible statistical model from the data available.
