---
output: 
  pdf_document:
    latex_engine: xelatex
    number_sections: true
#    pandoc_args: ["--output=Output/01-ProjectPlan.pdf"]
urlcolor: blue
linkcolor: black
header-includes:
  - \usepackage{color}
  - \usepackage{fancyhdr}
mainfont: Times New Roman
monofont: Times New Roman
sansfont: Times New Roman
---
\pagenumbering{gobble}

```{r child = '911-TitlePage.Rmd'}
```

\newpage
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0.4pt}


# High level description

```{r child = '912-Introduction.Rmd'}
```

# Resource needs

## Training requirements

```{r child = '913-TrainingRequirements.Rmd'}
```

## Tools & resources used

Fulfilling the completition need for the project the following tools are planned to be used:

```{r child = '871-Tools.Rmd'}
```


## Data sources

The project will use the following data provided by multiple US government agencies:

```{r child = '872-DataSources.Rmd'}
```

## Restrictions

Restrictions apply as per the restrictions set by the tools, data providers and owners of additional resources used. No addtional restrictions have been identified and set regarding the use of the results of this project.

## Contributors

```{r child = '860-Contributors.Rmd'}
```