---
title: "Final Paper"
subtitle: "for the CEU MSc in Business Analytics program"
author: "Gabor Horvath"
output: 
  pdf_document:
    latex_engine: xelatex
    number_sections: true
urlcolor: blue
linkcolor: blue
header-includes:
  - \usepackage{color}
  - \usepackage{fancyhdr}
mainfont: Times New Roman
monofont: Times New Roman
sansfont: Times New Roman
---
\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\thetitle}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0.4pt}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment=NA)
source("../90-UserDefinedFunctions.R")
suppressPackageStartupMessages(loadLibraries())
suppressPackageStartupMessages(readConfigFile(FALSE))
#source("../01-WildLiveStrikeDataSetDataPreparation.R")
#suppressPackageStartupMessages(wildLifeStrikeDataSet())
#source("../02-OnTimeFlightPerformanceDataSetDataPreparation.R")
#suppressPackageStartupMessages(onTimeFlightPerformanceDataSet())
#source("../03-WildLiveStrikeDataSetDataCleanup.R")
#suppressPackageStartupMessages(wildLifeStrikeDataSetDataCleanup())
#source("../04-OnTimeFlightPerformanceDataSetDataCleanup.R")
#suppressPackageStartupMessages(onTimeFlightPerformanceDataSetDataCleanup())
```




<!--




```{r create_pptx_sample}

# doc = pptx( )

# Slide 1 : Title slide
#+++++++++++++++++++++++
# doc <- addSlide(doc, "Title Slide")
# doc <- addTitle(doc,"Create a PowerPoint document from R software")
# doc <- addSubtitle(doc, "R and ReporteRs package")
# doc <- addDate(doc)
# doc <- addFooter(doc, "Isaac Newton")
# doc <- addPageNumber(doc, "1/4")

# Slide 2 : Add plot
#+++++++++++++++++++++++
# doc <- addSlide(doc, "Title and Content")
# doc <- addTitle(doc, "Bar plot")
# plotFunc<- function(){
#   barplot(VADeaths, beside = TRUE,
#           col = c("lightblue", "mistyrose", "lightcyan",
#                   "lavender", "cornsilk"),
#   legend = rownames(VADeaths), ylim = c(0, 100))
#   title(main = "Death Rates in Virginia", font.main = 4)
# }
# doc <- addPlot(doc, plotFunc )
# doc <- addPageNumber(doc, "2/4")

# Slide 3 : Add table 
#+++++++++++++++++++++++
# doc <- addSlide(doc, "Two Content")
# doc <- addTitle(doc,"iris data sets")
# doc <- addFlexTable(doc, FlexTable(iris[1:10,] ))
# doc <- addParagraph(doc, "iris data set gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica.")
# doc <- addPageNumber(doc, "3/4")

# Silde 4 : Add R script
#+++++++++++++++++++++
# doc <- addSlide(doc, "Content with Caption")
# doc <- addTitle(doc, "R Script for histogram plot")
# doc <- addPlot(doc, function() hist(iris$Sepal.Width, col=4))
# r_code ="data(iris)
# hist(iris$Sepal.Width, col = 4)"
# doc <- addRScript(doc, text=r_code)

# write the document 
# writeDoc(doc, "r-reporters-powerpoint.pptx" )

```

-->


---
references:
- id: shearer2000
  title: The CRISP-DM Model - The New Blueprint for Data Mining
  author:
  - family: Shearer
    given: Colin
  volume: 5
  number: 4
  publisher: Journal of Data Warehousing
  page: 13-22
  type: article-journal
  issued:
    year: 2000
    month: 9
---







